---
output:
  md_document:
    variant: markdown_github
---

# Exercise 4. Data Manipulation using DPLYR

<br>  

<b>Estimated time: </b>  
45 Minutes

<b>What this exercise is about</b>  
Perform the following operations using only the dplyr library. We will be reviewing the following operations: 

* filter (and slice()) 
* arrange() 
* select() (and rename())
* distinct() 
* mutate() (and transmute()) 
* summarise0 
* sample_n() and sample_frac()  

<b><br>
Requirernents:</b> RStudio 
```{r  echo=TRUE, results="hide"}
library(dplyr)
```

<br>
<b>  
Solve the following problerns using R
</b>

Q1. Return rows of cars that have an mpg value greater than 20 and 6 cylinders?
```{r}
df <- mtcars
filter(mtcars,mpg > 20 & cyl == 6)
```
<br>
Q2.  Reorder the Data Frame by cyl first, then by descending wt?
```{r}
data_set <- arrange(.data = df,cyl, desc(wt))
head(x = data_set,n = 10)
```
<br>
Q3. Select the columns mpg and hp?
```{r}
data_set <- select(.data = df, mpg, hp)
head(x = data_set,n = 10)
```
<br>
Q4. Select the distinct values ot the gear column?
```{r}
distinct(.data = df, gear)
```
<br>
Q5. Create a new column called "Performance" which is calculated by hp divided by wt?
```{r}
Performance <- df$hp/ df$wt
df <- mutate(.data = df,Performance)
```
<br>
Q6. What is the average mpg value for all the cars?
```{r}
summarise(.data = df,average = mean(mpg), n = n())
```
<br>
Q7. Use pipe operators to get the mean hp value for cars With 6 cylirxiers?
```{r}
df %>% filter(cyl == 6) %>% summarise(average = mean(hp), n =n())
```
<br>
Q8.Create two data frames?  
<br>
<table border =2 style="width:20%; text-align:center">
        <tr>
                <td>ID</td>
                <td>Salary</td>
        </tr>
        <tr>
                <td>1</td>
                <td>1000</td>
        </tr>
        <tr>
                <td>2</td>
                <td>2000</td>
        </tr>
        <tr>
                <td>3</td>
                <td>3000</td>
        </tr>
        <tr>
                <td>4</td>
                <td>4000</td>
        </tr>        
</table>
<br>
<table border =2 style="width:20%; text-align:center">
        <tr>
                <td>ID</td>
                <td>Bonus</td>
        </tr>
        <tr>
                <td>1</td>
                <td>200</td>
        </tr>
        <tr>
                <td>2</td>
                <td>300</td>
        </tr>
        <tr>
                <td>3</td>
                <td>500</td>
        </tr>
        <tr>
                <td>4</td>
                <td>700</td>
        </tr>
        <tr>
                <td>6</td>
                <td>800</td>
        </tr>
</table>
```{r}
sal <- data.frame(ID = 1:5, Salary = c(1000,2000,3000,4000,5000))
bon <- data.frame(ID = c(1,2,3,4,6), Bonus = c(200,300,500,700,800))
```
<br>
Q9. Write a code to idetify the ID who do not have salary?
```{r}
anti_join(x = bon,y = sal ,by = "ID")
```
<br>
Q10. Write a code to idetify the ID who do not have bonus?
```{r}
anti_join(x = sal,y = bon ,by = "ID")
```
<br>
Q11. Write a code to idetify the ID who have both salary and bonus?
```{r}
inner_join(x = sal,y = bon, by = "ID")
```
<br>
