---
output:
  md_document:
    variant: markdown_github
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/')
```

# Exercise 12.Visualization

<br>  

<b>Estimated time: </b>  
45 Minutes 

<b>What this exercise is about</b>  
For these exercises, use the GGPLOT2 library  

<b>
Requirernents:</b> RStudio 
```{r include=TRUE, results="hide"}
library(ggplot2)
```
<b>Solve the following problerns using R
</b>

Q1. Run ggplot(data = mpg) what do you see? 
```{r eval=FALSE }
ggplot(data = mpg)
```
It creates an empty plot. The ggplot() function only creates the background of the plot, there is no layers specified.   
<br>
Q2. How many rows are in mtcars? How many columns?.
```{r}
dim(mtcars)
```
32 rows and 11 columns.  
<br>
Q3. What does the drv variable describe? Read the help for ?mpg to find out
```{r eval=FALSE}
?mpg
```
It is a categorical variable used to define the type of drive train, where f = front-wheel drive, r = rear wheel drive, 4 = 4wd
<br>
Q4. Make a scatter plot of mpg vs. cyl
```{r Exercise 12 Visualization 1}
ggplot(data = mpg, mapping = aes(x = hwy, y = cyl)) + geom_point()
```
<br>
Q5. What happens if you make a scatter plot of class vs drv? Why is the plot not useful? 
```{r eval=FALSE}
ggplot(data = mpg, mapping = aes(x = class, y = drv)) + geom_point()
```
There are only few data points  
<br>
Q6. What's gone wrong with this code? Why are the points not blue?
```{r Exercise 12 Visualization 2}
ggplot(data = mpg)+
        geom_point(mapping = aes(x = displ,y = hwy,color = "Blue"))

```
Here since the colour attribute is given inside the aes "blue" passed to the color is considered as a catergorical varoable with single value "Blue". To change the color to blue the color attribute should be give outside the aes as a parameter of geom_ponit() 
<br>
Q7. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
```{r eval=FALSE}
?mpg
```
The following list contains the categorical variables

* model
* trans
* drv
* fl
* class

The following list contains the continuous variables

* displ
* year
* cyl
* city
* hwy

<br>