---
output:
  md_document:
    variant: markdown_github
---

# Exercise 2. Matrices

<br>  

<b>Estimated time: </b>  
20 Minutes

<b>What this exercise is about</b>  
Through these exercises we review the matrix data structure and perhaps introduce you to a few ideas for you to discover on your own.  

<b><br>
Requirernents:</b> RStudio 
<br>
<b>  
Solve the following problerns using R
</b>

Q1. Create 2 vectors A and B, where A is (1,2,3) and B is (4,5,6). With these vectors, use the cbind() or 'rbind() function to create a 2 by 3 matrix from the vectors. You'll need to figure Out which of these binding functions is the correct choice?
```{r}
a <- c(1,2,3)
b <- c(4,5,6)
rbind(a,b)
```
<br>
Q2. Create a 3 by 3 matrix consisting ot the numbers Create this matrix using the shortcut 19 and by specifying the nrow argument the matrix() function call. Assign this matrix to the variable mat?
```{r}
mat <- matrix(1:9, nrow = 3, ncol = 3, byrow = T)
```
<br>
Q3. Find the mean ot matrix created?
```{r}
mean(mat)
```
<br>
Q4. Find the standard deviation for the matrix?
```{r}
sd(mat)
```
<br>
Q5. Find the sum for the matrix?
```{r}
sum(mat)
```
<br>
Q6. Find the row sum for matrix?
```{r}
rowSums(mat)
```
<br>
Q7. Find the coloum sum for matrix?
```{r}
colSums(mat)
```
<br>
Q8. Find the row means for matrix?
```{r}
rowMeans(mat)
```
<br>
Q9. Confirm that mat is a matrix using is.rnatrix()
```{r}
is.matrix(mat)
```
<br>
Q10. Create a 5 by 5 matrix consisting of the numbers 1-25 and assign it to the variable mat2, The top row should the numbers 1-5?
```{r}
mat2 <- matrix(data = 1:25,nrow = 5,byrow = T)
```
<br>
Q11. Give the row names for the matrix as Day1, Day2..
```{r}
row.names(mat2) <- c("Day1","Day2","Day3","Day4","Day5")
```
<br>
Q12. Using indexing notation, grab a sub-section Of mat2 from the previous exercise mat looks like this  
[7,8]  
[12,13]  
```{r}
mat2[2:3,2:3]
```
<br>
Q13. Using indexing notation, grab a sub-section Of mat2 from the previous exercise mat looks like this  
[19,20]  
[24,25]  
```{r}
mat2[4:5,4:5]
```
<br>
Q14. What is the sum of all the elements in mat2?
```{r}
sum(mat2)
```
<br>
Q15. Find out how to use runif() to create a 4 by 5 matrix consisting of 20 random numbers (4*5=20)?
```{r}
matrix(data = runif(n = 20,min = 20,max = 100),nrow = 4)
```


