---
output:
  md_document:
    variant: markdown_github
---

# Exercise 3. Data Frames

<br>  

<b>Estimated time: </b>  
45 Minutes

<b>What this exercise is about</b>  
For this exercise we will test your knowledge of data frames

<b><br>
Requirernents:</b> RStudio 
<br>
<b>  
Solve the following problerns using R
</b>

Q1. Recreate the following datatrame by creating vectors and using the data-frame function?  
<br>
<table border =2 style="width:60%; text-align:center">
        <th>
                <td>Age</td>
                <td>Weight</td>
                <td>Sex</td>
        </th>
        <tr>
                <td>Sam</td>
                <td>22</td>
                <td>150</td>
                <td>M</td>
        </tr>
        <tr>
                <td>Frank</td>
                <td>25</td>
                <td>160</td>
                <td>K</td>
        </tr>
        <tr>
                <td>Amy</td>
                <td>26</td>
                <td>120</td>
                <td>F</td>
        </tr>
</table>
```{r}
name <- c("Sam","Frank","Amy")
Age <- c(22,25,26)
Weight <- c(150,160,120)
Sex <- c("M","F","K")
df <-data.frame(row.names = name,Age,Weight,Sex)
df
```
<br>
Q2. Check if mtcars is a dataframe using is.data.frame()?
```{r}
is.data.frame(df)
```
<br>
Q3. Use as.data.frame() to convert a matrix into a dataframe?
```{r}
mat <- matrix(data = 1:25,nrow = 5,byrow = T)
as.data.frame(mat)
```
<br>
Q4. Set the built-in data frame mtcars as a variable df. We'll use this df variable for the rest of the exercises. 
```{r}
df <- mtcars
```
<br>
Q5. Display the first 6 rows Of df?
```{r}
head(df)
```
<br>
Q6. What is the average mpg value for all the cars?
```{r}
mean(df$mpg)
```
<br>
Q7. Select the rows where all cars have 6 cylinders (cyl column)?
```{r}
df[df$cyl==6,]
```
<br>
Q8. Select the columns am,gear, and cart?
```{r}
df[,c("am","gear","carb")]
```
<br>
Q9. Create a new column called performance. which is calculated by hp/wt?
```{r}
df["Performance"] <- df$hp/df$wt
```
<br>
Q10. Your performance column will have several decimal place precision. Figure out how to use round() (check help(round)) to reduce this accuracy to only 2 decimal places?
```{r}
df$Performance <- round(df$Performance,2)
```
<br>
Q11. What is the average mpg for cars that have more than 100 hp AND a value Of more than 2.5?
```{r}
mean(subset(x = df, hp>100 & wt >2.5)$mpg)
```
<br>
Q12. What is the mpg of the Hornet Sponabout?  
```{r}
df["Hornet Sportabout",]$mpg
```
