---
output:
  md_document:
    variant: markdown_github
---

```{r global_options}
knitr::opts_chunk$set(fig.path='Figs/')
```
# Exercise 5. Case study using GGPLOT

<br>  

<b>Estimated time: </b>  
150 Minutes

<b>What this exercise is about</b>  
For this optional assignment we will be recreating this plot from The Economist: Feel free to work through as little Or as much as you want.  
<br>
This assignrnent Will be very challenging! You Will recreate this plot by following the Steps outlined in bold below. You Will need to reference documentation! There are things in this plot that we have purposefully not covered to test your skills in going to the documentation and referencing what you need to know. Links and hints will provided to along way!. 

<b><br>
Requirernents:</b> RStudio and GGPLOT
```{r  echo=TRUE, results="hide"}
library(ggplot2)
library(dplyr)
```

<br>
<b>  
Solve the following problerns using R
</b>

Import the ggplot2 data.table libraries and use fread to load the csv file 'Economist_Assignment_Data.csv' into a dataframe called df ?
```{r}
df <- read.csv("datasets/Economist_Assignment_Data.csv")[-1]
```
<br>
Check the head of df?
```{r}
head(df)
```
<br>
Use ggplot() + geom_plot() to create a scatter plot object called pl. You Will need to specify x=CPl and y=HDI and color=Region as aesthetics
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + 
     geom_point()
```
<br>

Change the points to be larger empty circles. (You'll have to go back and add arguments to geom_point() and reassign it to Pl.) You'll need to figure out what shape = and size =
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + 
     geom_point(shape = 1, size=3)
```
<br>
Add geom_smooth(aes(group=1)) to add a trend line
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + 
     geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1))
```
<br>
We want to further edit this trend line. Add the following arguments to geom_smooth (outside of aes):  

* method = 'lm'
* formula = y log(x) 
* se = FALSE 
* color = red
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + 
     geom_point(shape = 1, size=3) +    
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x))


```
<br>
It's really starting to look similar! But we still need to add labels, we can use geom text! Add geom_text(aes(label = Country)) and see what happens (Hint: It should be way too many labels)
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + 
     geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x)) +
     geom_text(aes(label=Country))
```
<br>
Label the subset of the plot 
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + 
     geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x)) +
     geom_text(data = filter(df,Country 
     %in%   c("Congo","India","Greece","Russia","Iraq","China","Norway","France","Argentina","Barbados")),
     aes(label =Country),size = 4,color= "black")
```
<br>
Almost there! Still not perfect, but good enough for this assignment. Later on we'll see why interactive plots are better for labeling. Now let's just add some labels and a theme, set the x and y scales and we're done!  
Add theme_bw() to your plot
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x)) +
     geom_text(data = filter(df,Country 
     %in% c("Congo","India","Greece","Russia","Iraq","China","Norway","France","Argentina","Barbados")),
     aes(label =Country),size = 4,color= "black") +
     theme_bw()
```
<br>
Add scale_x_continuous0 and set the following arguments: 

* name = Same x axis as the Economist Plot 
* limits = Pass a vector of agpropriate x limits
* breaks = 1:10
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x)) +
     geom_text(data = filter(df,Country 
     %in% c("Congo","India","Greece","Russia","Iraq","China","Norway","France","Argentina","Barbados")),            
     aes(label =Country),size = 4,color= "black") +
     theme_bw() + 
     scale_x_continuous(name = "Corruption Perception Index",breaks = 1:10)
```
<br>
Now use scale_y_continuous() to do similar operations to the y axis! 
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x)) +
     geom_text(data = filter(df,Country 
     %in% c("Congo","India","Greece","Russia","Iraq","China","Norway","France","Argentina","Barbados")),            
     aes(label =Country),size = 4,color= "black") +
     theme_bw() + 
     scale_x_continuous(name = "Corruption Perception Index",breaks = 1:10) +
     scale_y_continuous(name = "Human Development Index, 2011(1=Best)",limits = c(.2,1))
```
<br>
finally use ggtitle() to add a sring as a title
```{r}
ggplot(data = df,mapping =aes(x = CPI,y = HDI,color= Region)) + geom_point(shape = 1, size=3) +
     geom_smooth(aes(group=1), color ="red", method = "lm",se=F, formula = y~log(x)) +
     geom_text(data = filter(df,Country 
     %in% c("Congo","India","Greece","Russia","Iraq","China","Norway","France","Argentina","Barbados")),            
     aes(label =Country),size = 4,color= "black") +
     theme_bw() + 
     scale_x_continuous(name = "Corruption Perception Index",breaks = 1:10) +
     scale_y_continuous(name = "Human Development Index, 2011(1=Best)",limits = c(.2,1)) +
     ggtitle(label = "           Corruption and Human Development")
```
<br>
