---
output:
  md_document:
    variant: markdown_github
---

# Exercise 8. Matrices Advanced 

<br>  

<b>Estimated time: </b>  
60 Minutes 

<b>What this exercise is about</b>  
For these exercises, use the learnings of matrices

<b>
Requirernents:</b> RStudio 
  
<b>Solve the following problerns using R
</b>

Q1. Suppose  

$$
A = \left(\begin{array}{cc} 
1 & 1 & 3 \\
5 & 2 & 6 \\
-2 & -1 & -3
\end{array}\right)
$$ 
a. Check that A 3 = 0 where 0 is a 3 * 3 matrix with every entry equal to 0?
```{r}
tmp <- matrix(data = c(1,1,3,5,2,6,-2,-1,-3), byrow = T, nrow = 3)
tmp%*%tmp%*%tmp
```
<br>
b. Replace the third column Of A by the sum Of the second and third columns
```{r}
tmp[,3] <- tmp[,1]+tmp[,2]
tmp
```
<br>
Q2. Create the following matrix B with 15 rows

$$
B = \left(\begin{array}{cc} 
10 & -10 & 10 \\
10 & -10 & 10 \\
... & ... & ... \\
10 & -10 & 10
\end{array}\right)
$$ 
Calculate the 3 * 3 matrix B TB. (Look at the help for crossprod)?
```{r}
B <- matrix(data = rep(c(10,-10,10),15), nrow = 15,byrow = T)
t(B)%*%B
crossprod(B)
```
<br>
Q3. Create a 6 * 6 matrix matE with every entry equal to 0. Check what the functions row and col return when applied to matE. Hence create the 6 6 matrix:
$$
B = \left(\begin{array}{cc} 
0 & 1 & 0 & 0 & 0 & 0 \\
1 & 0 & 1 & 0 & 0 & 0 \\
0 & 1 & 0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 & 1 & 0 \\
0 & 0 & 0 & 1 & 0 & 1 \\
0 & 0 & 0 & 0 & 1 & 0 
\end{array}\right)
$$ 
```{r}
matE <- matrix(data = 0, nrow = 6,ncol = 6)
matE[abs(col(matE) - row(matE)) == 1] <- 1
matE
```
<br>
Q4. Look at the help for the Outer. Hence create the following patterned matrix?
$$
\left(\begin{array}{cc} 
0 & 1 & 2 & 3 & 4 \\
1 & 2 & 3 & 4 & 5 \\
6 & 3 & 4 & 5 & 6 \\
3 & 4 & 5 & 6 & 7 \\
4 & 5 & 6 & 7 & 8
\end{array}\right)
$$ 
```{r}
outer(0:4,0:4,'+')
```
<br>
Q5. Creating the following patterned matrices. in each case, your solution should make use of the
special form of the matrix - this means that the solution should easily generalise to creating a larger matrix with the same structure and should not involve typing in all the entries in the matrix
$$
(a)\left(\begin{array}{cc} 
0 & 1 & 2 & 3 & 4 \\
1 & 2 & 3 & 4 & 0 \\
2 & 3 & 4 & 0 & 1 \\
3 & 4 & 0 & 1 & 2 \\
4 & 0 & 1 & 2 & 3
\end{array}\right)
      \
(b)\left(\begin{array}{cc} 
0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 0 \\
: & : & : & : & : & : & : & : & : & : \\
8 & 9 & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
9 & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
\end{array}\right)
\\
(c)\left(\begin{array}{cc} 
0  &  8  &  7  &  6  &  5  &  4  &  3  &  2  &  1 \\
1  &  0  &  8  &  7  &  6  &  5  &  4  &  3  &  2 \\
2  &  1  &  0  &  8  &  7  &  6  &  5  &  4  &  3 \\
3  &  2  &  1  &  0  &  8  &  7  &  6  &  5  &  4 \\
4  &  3  &  2  &  1  &  0  &  8  &  7  &  6  &  5 \\
5  &  4  &  3  &  2  &  1  &  0  &  8  &  7  &  6 \\
6  &  5  &  4  &  3  &  2  &  1  &  0  &  8  &  7 \\
7  &  6  &  5  &  4  &  3  &  2  &  1  &  0  &  8 \\
8  &  7  &  6  &  5  &  4  &  3  &  2  &  1  &  0 \\
\end{array}\right)
$$ 
(a)
```{r}
outer(X = 0:4,Y = 0:4,FUN = "+") %% 5
```
<br>
(b)
```{r}
outer(X = 0:9,Y = 0:9,FUN = "+") %% 10
```
<br>
(c)
```{r}
outer(X = 0:8,Y = 0:8,FUN = "-") %% 9
```
<br>
Q6. Solve the following system of linear equations in five unknowns   
x + 2y + 3z + 4p + 5q = 7  
2x + y + 2z + 3p + 4q = -1  
3x + 2y + z + 2p + 3q = -3  
4x + 3y + 2z + p + 2q = 5  
5x + 4y + 3z + 2p + q = 17  
```{r}
A <- matrix(data = c(1,2,3,4,5,2,1,2,3,4,3,2,1,2,3,4,3,2,1,2,5,4,3,2,1),byrow = TRUE, ncol = 5)
B <- matrix(data = c(7,-1,-3,5,17))
solve(A) %*% B #or
solve(a = A,b = B)
```
<br>
Checking if the obtained output is correct
```{r}
A %*% solve(a = A,b = B)
```

